\documentclass[15pt,oneside,reqno]{amsart} 
\input{preamble}

\newcommand{\isMainDocument}{} % 各sectionに影響を与えるフラグを設定

\begin{document}
\maketitle

\begin{abstract}
Jarossay introduced adjoint multiple zeta values, and he found $\Q$-algebraic relations among adjoint multiple zeta values, referred to as the \emph{adjoint double shuffle relations}, by using Racinet's dual formulation of the generating series of multiple zeta values.
Jarossay defined the affine scheme $\AdDMR_0$ determined by the adjoint double shuffle relations and posed a question whether $\AdDMR_0$ is isomorphic to Racinet's double shuffle group $\DMR_0$. 
In this paper, we refine Jarossay's question by formulating what we call the adjoint conditions and by addressing its Lie algebraic side. 
Within this framework, we construct the Lie algebra associated with the adjoint double shuffle relations by imposing Hirose's parity results.
%Our main theorem provides the first nontrivial algebraic structure from the $\Q$-linear relations among adjoint multiple zeta values.
%We then give an isomorphism of $\Q$-linear spaces obtained by a bigraded version of the double shuffle relations and that of the adjoint double shuffle relations.
\end{abstract}

\tableofcontents

\input{section1.tex}

\input{Algebraic_setup.tex}

\input{Extended_double_shuffle_relations_and_DMR.tex}

\input{Generalized_SMZVs_and_AdDMR.tex}

\input{Main_Theorem.tex}

\input{A_proof_of_main_theorem.tex}

\input{Conclusion_remarks}

\input{Proof_of_lemma}

\input{Computical_calculations}




\begin{center}
\textbf{Acknowledgments}
\end{center}

The author would first like to express his deepest gratitude to Professor Minoru Hirose. Without his kindness and encouragement, the author would not have been able to establish the main theorem in this paper.  
He is also grateful to Dr. Nao Komiyama for giving him valuable advice on the theory of commutative power series.  
He would like to thank Dr. Annika Burmester, Prof. Henrik Bachmann, Prof. Hidekazu Furusho, Prof. David Jarossay, Dr. Iu-Iong, Ng, Prof. Koji Tasaka, and Dr. Khalef Yaddaden for their helpful comments on his paper.
The author thanks Takeshi Shinohara, Kosei Watanabe, and Ku-Yu Fan for reviewing the Main Theorem.
%\textcolor{white}{The author thanks Hidekazu Furusho for his insightful comment. Namely, “It is just an embedding. This work has no effect.”}


\bibliographystyle{amsplain}
\bibliography{reference-adjoint}


\end{document}


