\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[spanish,english]{babel}
\usepackage[pdfborder={0 0 0}]{hyperref}
\usepackage{subcaption}
%\usepackage[document]{ragged2e}
\usepackage{graphicx}
%\usepackage{enumitem}
%\usepackage{todonotes}
%\usepackage[disable]{todonotes}

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{listings}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

%\setenumerate[0]{label*=(\alph*)}

% math
\usepackage{amsmath}
%\usepackage{biblatex}
\usepackage{xcolor, soul}
\sethlcolor{green}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{bm}  
\usepackage{amsthm}
\usepackage{tikz-cd}
\usepackage{tikz}
\usetikzlibrary{cd}
%\usepackage[square, numbers]{natbib}
\usetikzlibrary{cd}
\newtheorem{thm}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\newtheorem*{cor*}{Corolario}
\newtheorem*{thm*}{Theorem}
\newtheorem{exc}{Excercise}
\newtheorem{ex}[thm]{Example}
\newtheorem{claim}[thm]{Afirmación}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{prop}{Proposition}
\newtheorem*{prop*}{Proposition}
\newtheorem{obs}{Observación}
\theoremstyle{remark}
\newtheorem{rem}{\textbf{Remark}}
\theoremstyle{remark}
\newtheorem*{conj}{Conjetura}
\DeclareMathOperator{\End}{End}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Id}{Id}
\DeclareMathOperator{\Stab}{Stab}
\DeclareMathOperator{\img}{im}
\DeclareMathOperator{\Gr}{Gr}
\DeclareMathOperator{\Diff}{Diff}
\DeclareMathOperator{\Deck}{Deck}
\DeclareMathOperator{\Lie}{Lie}
\DeclareMathOperator{\Ad}{Ad}
\DeclareMathOperator{\ad}{ad}
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\Der}{Der}
\DeclareMathOperator{\PSL}{PSL}
\DeclareMathOperator{\Ob}{Ob}
\DeclareMathOperator{\dR}{dR}
\DeclareMathOperator{\vol}{vol}
\DeclareMathOperator{\Vol}{Vol}
\DeclareMathOperator{\Ric}{Ric}
\renewcommand{\div}{\operatorname{div}}
\DeclareMathOperator{\grad}{grad}
\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\pr}{pr}
\newcommand{\K}{\mathbb{K}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Hn}{\mathbb{H}^n}
\newcommand{\D}{\mathbb{D}}
\newcommand{\partialt}{\frac{\partial}{\partial t}}
\newcommand{\partials}{\frac{\partial}{\partial s}}
\renewcommand{\L}{\mathcal{L}}
\renewcommand{\H}{\mathbb{H}}
\newcommand{\metric}{\left\langle - , -\right\rangle}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\uHom}{\underline{\operatorname{Hom}}}
\newcommand{\etop}{\mathbf{e}_{\text{top}}}
\newcommand{\egeo}{\mathbf{e}_{\text{geo}}}
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\newcommand{\M}{\Tilde{M}}
\renewcommand{\P}{\mathbb{P}}
\renewcommand{\Im}{\operatorname{Im}}
\newcommand{\GL}{\operatorname{GL}}
\newcommand{\SL}{\operatorname{SL}}
\newcommand{\Isom}{\operatorname{Isom}}
%\renewcommand{\phi}{\varphi}
\renewcommand{\hom}{\operatorname{Hom}}
\newcommand{\del}[1]{\frac{\partial}{\partial #1}}
\newcommand{\dell}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\sign}{\operatorname{sign}}
\newcommand{\subin}{\mathbin{\rotatebox[origin=c]{-180}{\reflectbox{$\neg$}}}}
\newcommand{\g}{\mathfrak{g}}
\newcommand{\h}{\mathfrak{h}}
\newcommand{\gl}{\mathfrak{gl}}
\DeclareMathOperator{\Rm}{Rm}
\DeclareMathOperator{\inj}{inj}
\DeclareMathOperator{\diam}{diam}
\DeclareMathOperator{\dil}{dil}
\DeclareMathOperator{\In}{in}
\DeclareMathOperator{\trop}{trop}
\newcommand{\I}{\mathcal{I}}
\newcommand{\V}{\mathfrak{v}}
\renewcommand{\a}{\mathbf{a}}
\renewcommand{\b}{\mathbf{b}}
\newcommand{\x}{\mathbf{x}}
\newcommand{\y}{\mathbf{y}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\xa}{{\x}^{\a}}
\newcommand{\xb}{{\x}^{\b}}
\renewcommand{\sl}{\mathfrak{sl}}
\DeclareMathOperator{\hht}{ht}
\newcommand{\n}{\mathfrak{n}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\p}{\mathbf{p}}
\newcommand{\m}{\mathbf{m}}
\DeclareMathOperator{\Ht}{ht}
\newcommand{\U}{\mathbf{u}}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\Mon}{Mon}
\DeclareMathOperator{\im}{im}

\clubpenalty=250

\title{Birational sequences for the Grassmannian $\Gr\left(3,n\right)$}
\author{Joaquin Torres Henestroza}
\date{2025}


\begin{document}

\maketitle
\begin{abstract}
    Following the ideas of Bossinger and Fang, Fourier, and Littelman, we study \emph{iterated sequences} for the Grassmannian $\Gr\left(3,n\right)$ as a special class of birational sequences. For each iterated sequence, there is a weighting matrix $M_S$ corresponding to a valuation on the rational coordinate ring and we show that the initial form of a Plücker relation $\In_{M_S}\left(R_{I,J}\right) $ is binomial. We show that, in some cases, the cones $C_S$ in the tropical Grassmannian that satisfy $\In_{M_S}\left(\I_{3,n}\right)=\In_{C_S}\left(\I_{3,n}\right)$ only depend on the first two indices used in each iteration. In the case of $\Gr\left(3,6\right)$, these cones are obtained computationally and are classified up to automorphism induced by the symmetric group $S_6$.  
\end{abstract}
\medskip
\noindent
\textbf{MSC (2020):} 14M15, 14D06.


\tableofcontents

\vspace{0,5cm} 

In the context of algebraic geometry, toric varieties are especially popular for their connections between their geometric properties and combinatorial objects associated to them. These connections can be extended to certain projective varieties if there exists a \emph{toric degeneration}. Formally, given a (projective) variety $X$, a \emph{toric degeneration} is a flat family $\pi:\mathcal{X}\rightarrow \mathbb{A}_{\C}^1$ such that $\pi^{-1}\left(t\right)$ is isomorphic to $X$ for $t\neq 0$, and $\pi^{-1}\left(0\right)$ is a toric variety. If a variety $X$ admits said degeneration, then both $X$ and the toric variety $\pi^{-1}\left(0\right)$ share common properties (cf. \cite{bossinger2023surveytoricdegenerationsprojective}), thus the next questions to ask are: for which varieties is it possible to construct such degenerations and how can these degenerations actually be constructed? 

In pursuit of partial answers to these questions, the goal of this paper is the construction of toric degenerations which arise as Gröbner degenerations of the Grassmannian $\Gr\left(3,n\right)$. In order to do this, the usual approach is computing initial ideals of the Plücker ideal $\I_{3,n}$ with respect to weight vectors in the tropical Grassmannian $\trop\left(\Gr(3,n)\right)$. Thus, the problem of finding degenerations reduces, in this case, to finding constructions of weight vectors. In the case of the Grasmannian $\Gr\left(3,6\right)$ such constructions can be done, for example, using plabic graphs (cf. \cite{bossinger2016toricdegenerationsgr2ngr36}), matching fields (cf. \cite{Mohammadi_2019}), or by considering \emph{birational sequences}: for $n\geq 4$, let $\Phi$ denote the $\mathbf{A}_{n-1}$ type root system and for each positive root $\beta\in \Phi^+$, consider the one-parameter root subgroup $U_{\beta}\subset U^+$, then a sequence of positive roots $S= \left(\beta_1,\dots,\beta_N\right)$ is a \emph{birational sequence} for $\Gr\left(3,n\right)$ if the multiplication map
\begin{equation*}
    \psi_S := \operatorname{mult}:U_{\beta_N}\times \dots \times U_{\beta_1} \rightarrow U^+
\end{equation*} has image birational to $\Gr\left(3,n\right)$ (see Definition \ref{birseqs}). This last approach, introduced by Fang, Fourier, and Littelman in \cite{FANG2017107} and for the case of a Grassmannian by Bossinger (cf. \cite{Bossinger:2021}), allows to give coordinates on the Grassmannian that gives rise to a valuation on the rational coordinate ring $\C\left(\Gr(3,n)\right)\setminus \lbrace 0\rbrace$, and thus to the weighting matrix $M_S$. By \cite[Theorem 1]{Bossinger:2021}, there is a weight vector $w_S\in \trop\left(\Gr(3,n)\right)$ such that the initial ideal with respect to $M_S$ and the initial ideal with respect to $w_S$ coincide: $\In_{w_S}\left(\I_{3,n}\right) = \In_{M_S}\left(\I_{3,n}\right)$. 

In \cite[Definition 11]{Bossinger:2021}, the special class of \emph{iterated sequences} is introduced. This special kind of birational sequences have the advantage that they are constructed inductively, and therefore the calculations can be implemented computationally. This advantage is used for arbitrary Grassmannians $\Gr(3,n)$, first in Lemma \ref{homogeneidad} and Corollary \ref{only-depends-on-lex}. A direct consequence of these results is Proposition \ref{binomial}. 

\begin{prop*}
    Let $S$ be an iterated sequence for $\Gr\left(3,n\right)$ and $R_{I,J}\neq 0$ a Plücker relation (see Equation \ref{PR}). Then its initial form $\In_{M_S}\left(R_{I,J}\right)$ is binomial.
\end{prop*}

The construction of weight vectors in the tropical Grassmannian relies on the construction of \emph{order preserving projections} (see Section \ref{sec3}). Since order preserving projections must preserve the inequalities obtained when computing the initial forms of Plücker relations (with respect to a weighting matrix $M_S$), a first step in the classification of initial ideals with respect to weighting matrices is given by Propositions  \ref{perm-equality} and \ref{change-equality}.

\begin{prop*}
    Let $S_1$ and $S_2$ be two iterated sequences for $\Gr\left(3,n\right)$. Assume that the first two indices used in each iteration coincide. Given a projection $e_{S_1}:\Z^{3(n-3)}\rightarrow \Z$ that preserves inequalities with respect to $S_1$, there exists a projection $e_{S_2}:\Z^{3(n-3)}\rightarrow \Z$ that preserves inequalities with respect to $S_2$, and satisfies
    \begin{equation*}
        e_{S_1}M_{S_1} = e_{S_2}M_{S_2}. 
    \end{equation*}
\end{prop*}

In the $\Gr\left(3,6\right)$ case, the computations are done by implementing Algorithm \ref{algorithm} to find all inequalities arising from the initial forms of Plücker relations and \verb|polymake| (see \cite{polymake:2000}) to compute the weight vectors; then, the initial ideals are computed  and classified, up to the action of $S_6$, using \verb|macaulay2| (see \cite{M2}). The results are the contents of Theorems \ref{prim-class}, \ref{second_class}, and Corollary \ref{class_toric}, briefly stated below.

%%%%5
% Agregar aquí lo de las graficas y eso
%In \cite[Remark 1]{Bossinger:2021} it is summarized that the toric degenerations for $\Gr\left(2,n\right)$ by considering vectors $w\in \trop\left(\Gr(2,n)\right)$, the degenerations by considering plabic graphs, and the degenerations by considering \emph{iterated} sequences coincide. By \cite[Proposition 5.5]{speyer2003tropicalgrassmannian}, there exist vectors $w\in \trop\left(3,6\right)$ such that the initial ideal $\In_{w}\left(\I_{3,6}\right)$ is not prime, and thus, it does not induce a toric degeneration. Furthermore, for certain plabic graphs for $\Gr\left(3,6\right)$, it is the case that the ideal is not toric, as is mentioned in \cite[$\S7$]{bossinger2016toricdegenerationsgr2ngr36}. Therefore, the aforementioned equivalence between degenerations induced by 

\begin{thm*}
    Let $\mathcal{S}_{3,6}:=\left\lbrace \textrm{iterated sequences for }\Gr(3,6)\right\rbrace$. The map $S\mapsto \In_{M_S}\left(\I_{3,6}\right)$ is a map
    \begin{equation*}
        \mathcal{S}_{3,6}\rightarrow \left\lbrace \textrm{initial toric ideals of }\Gr(3,6)\right\rbrace.
    \end{equation*} The image has cardinality $\#\left\lbrace \In_{M_S}(\I_{3,6}):S\in \mathcal{S}_{3,6}\right\rbrace=240$. Under the action of $S_6\leq \operatorname{Aut}(\I_{3,6})$, there exist in $\left\lbrace \In_{M_S}(\I_{3,6}):S\in \mathcal{S}_{3,6}\right\rbrace$ 4 different equivalence classes $O_1,O_2,O_3,$ and $O_4$, listed with its cardinalities and its corresponding isomorphism classes
\begin{table}[H]
    \centering
    \begin{tabular}{|c|c|c|}
        \hline
        Orbit & $\#$ & Isomorphism class \\
        \hline
        $O_1\cap\mathbb{I}_{3,6}$ & $48$ & $ EEFF1 $\\
        \hline
        $O_2\cap\mathbb{I}_{3,6}$ & $48$ & $EFFG$ \\
        \hline 
        $O_3\cap\mathbb{I}_{3,6}$ & $48$ & $EEFF2$\\
        \hline
        $O_4\cap\mathbb{I}_{3,6}$ & $96$ & $EEFG$\\
        \hline
    \end{tabular}
    \caption*{Classification of the $G$-orbits in $\mathbb{I}_{3,6}$}
\end{table}

    Furthermore, every iterated sequence induces a toric degeneration of $\Gr\left(3,6\right)$, and these are classified according to the isomorphism classes mentioned above.
\end{thm*}

In order to present and prove these results, the paper is divided as follows: in Section \ref{sec1}, the notation and fundamental definitions and results are introduced; in Section \ref{sec2} the birational and iterated sequences are defined, the lowest-term valuation is defined, a proof of Lemma \ref{homogeneidad} is given and Algorithm \ref{algorithm} is described; finally, in Section \ref{sec3} the main results are presented.

\textbf{Acknowledgements:} The results presented in this paper are part of my BSc thesis supervised by Lara Bossinger at the Universidad Nacional Autónoma de México (UNAM). I am grateful for her advice and support during the realization of this work. I would also like to thank Juan González López for his help during the computational implementation.


\input{section1}

\input{section2}

\input{section3}

\bibliographystyle{alpha}
\bibliography{biblio}

J. TORRES HENESTROZA: Facultad de Ciencias, Universidad Nacional Autónoma de México, Investigación Científica, C.U., Alcaldía Coyoacán, C.P. 04510. Ciudad de México, México.

\emph{E-mail address}: \verb|joaquinth@ciencias.unam.mx|

\end{document}