\begin{thebibliography}{99}



\bib{CRB}{book}{%
      label={ADHL},% ← this forces the printed tag to ADHL
      author={Arzhantsev, I. and Derenthal, U. and Hausen, J. and Laface, A.},
      title={Cox Rings},
      note = {ISBN: 978-1-107-02462-5},
      series={Cambridge Studies in Advanced Mathematics},
      publisher={Cambridge University Press},
      place={Cambridge},
      year={2014}% ← no trailing comma here
    }




\bib{Borelli}{article}{
	label= {Bor},
	author={Borelli, M.},
	title={Divisorial varieties},
	journal={Pacific J. Math.},
	volume={13},
	date={1963},
	pages={375--388},
    doi = {10.2140/pjm.1963.13.375}
}


\bib{Bosch}{book}{
    label = {Bos},
	author={Bosch, S.},
	title={Algebraic geometry and commutative algebra},
	series={Universitext},
	publisher={Springer-Verlag},
	date={2022},
	note={ISBN: 978-1-4471-7522-3 },
}

\bib{BS}{article}{
    label = {BS},
	author={Brenner, H.},
	author={Schr\"{o}er, S.},
	title={Ample families, multihomogeneous spectra, and algebraization of
		formal schemes},
	journal={Pacific J. Math.},
	volume={208},
	date={2003},
	number={2},
	pages={209--230},
	doi={10.2140/pjm.2003.208.209},
}

\bib{CLS}{book}{
    label = {CLS},
  title={Toric Varieties},
  author={Cox, D.A.},
  author={Little, J.B.},
  author={Schenck, H.K.},
  series = {Grad. Stud. Math.},
 volume = {124},
 note = {ISBN: 978-0-8218-4819-7},
 year = {2011},
 publisher = {Providence, RI: American Mathematical Society (AMS)}
}

\bib{Cox}{article}{
    label = {C},
	author={Cox, D. A.},
title = {Erratum to ``{The} homogeneous coordinate ring of a toric variety''},
	journal={J. Algebraic Geom.},
	 volume = {23},
 number = {2},
 pages = {393--398},
 year = {2014},
 doi = {10.1090/S1056-3911-2013-00651-7}
}

\bib{Dade80}{article}{
label = {D},
author = {Dade, E. C.},
journal = {Mathematische Zeitschrift},
pages = {241-262},
title = {Group-Graded Rings and Modules},
volume = {174},
year = {1980},
doi = {10.1007/BF01161413}
}


\bib{SGA3}{book}{
    label = {SGA3},
  title={Sch{\'e}mas en groupes I (SGA 3): S{\'e}minaire de g{\'e}om{\'e}trie alg{\'e}brique du Bois Marie, 1962-64 : un s{\'e}minaire},
  author={Demazure, M. },
  author = {Grothendieck, A.},
edition = {New annotated edition of the 1970 original published by {Springer}},
  volume = {8},
  note={ISBN: 978-2-85629-324-9},
   series = {Doc. Math. (SMF)},
  year={2011},
   publisher = {Paris: Soci{\'e}t{\'e} Math{\'e}matique de France}
}




\bib{Wed}{book}{
    label = {GW},
  title={Algebraic Geometry I: Schemes: With Examples and Exercises},
  author={G\"{o}rtz, U.},
  author={Wedhorn, T.},
  note={ISBN: 978-3-8348-0676-5},
  series={Springer Studium Mathematik - Master},
  year={2020},
  publisher={Springer Fachmedien Wiesbaden}
}


\bib{Hartshorne}{book}{
 label = {Har},
  title={Algebraic Geometry},
  author={Hartshorne, R.},
 note={ISBN: 3-540-90244-9},
  series={Graduate Texts in Mathematics},
  year={1977},
  publisher={Springer-Verlag}
}


%\bib{HK}{article}{
% label = {HK},
%	author={Hu, Yi},
%	author={Keel, Sean},
%	title={Mori dream spaces and GIT},
%	journal={Michigan Math. J.},
%	volume={48},
%	date={2000},
%	pages={331--348},
%	doi={10.1307/mmj/1030132722},
%}



\bib{Hos}{misc}{
    label = {Hos},
  author        = {Hoskins, V.},
  title         = {Moduli problems and Geometric Invariant Theory},
  month         = {February},
  year          = {2016},
  publisher={Freie Universität Berlin}
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\bib{KU}{article}{
    label={KU},
author={K\"uronya, A.},
	author={Urbinati, Stefano},
	title={Geometry of multigraded rings and embeddings into toric varieties},
	    year={2019},
%     eprint={1912.04374},
      note={https://arxiv.org/abs/1912.04374, preprint}
	} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bib{Liu}{book}{
 label = {L},
  title={Algebraic Geometry and Arithmetic Curves},
  author={Liu, Q.},
  note={ISBN: 978–0–19–850284–5},
  series={Oxford graduate texts in mathematics},
  year={2002},
  publisher={Oxford University Press}
}

\bib{May}{article}{
    label = {MR},
      title={On multi-graded Proj schemes}, 
      author={A. Mayeux and S. Riche},
      year={2024},
%      eprint={2310.13502},
      note={https://arxiv.org/abs/2310.13502, preprint}
}

\bib{MFK}{book}{
    label = {MFK},
  title={Geometric Invariant Theory},
  author={Mumford, D.},
  author={Fogarty, J.},
  author={Kirwan, F.},
  note={ISBN: 3-540-56963-4},
   series = {Ergeb. Math. Grenzgeb.},
  year={1994},
 publisher = {Springer-Verlag},
}

\bib{Milne}{book}{
 label = {M},
  title={Algebraic Groups: The Theory of Group Schemes of Finite Type over a Field},
  author={Milne, J.S.},
  note={ISBN: 978-1-107-16748-3},
  series={Cambridge Studies in Advanced Mathematics},
  year={2017},
  publisher={Cambridge University Press}
}


\bib{Rob}{book}{
 author = {Roberts, P. C.},
 title = {Multiplicities and {Chern} classes in local algebra},
% edition = {Paperback reprint of the hardback edition 1998},
% fseries = {Cambridge Tracts in Mathematics},
 series = {Camb. Tracts Math.},
% issn = {0950-6284},
 volume = {133},
note = {ISBN: 978-0-521-06583-2},
 year = {2008},
 publisher = {Cambridge: Cambridge University Press},
% language = {English},
% keywords = {13H15,13-02,14C25,13D40},
% zbMATH = {5296404},
% Zbl = {1139.13012}
}



\bib{stacks-project}{book}{,
    label = {SP},
  author       = {The {Stacks project authors}},
  title        = {The Stacks project},
  note = {\url{https://stacks.math.columbia.edu}},
  year         = {2025},
}


\bib{Water}{book}{
    label = {W},
  title={Introduction to Affine Group Schemes},
  author={Waterhouse, W.C.},
  note={ISBN: 978-1-4612-6219-0},
  series={Graduate Texts in Mathematics},
  year={1979},
  publisher={Springer-Verlag}
}




\end{thebibliography}





%\bib{Gille}{article}{
%      title={When is a reductive group scheme linear?}, 
%      author={Philippe Gille},
 %     year={2021},
%      eprint={2103.07305},
%      archivePrefix={arXiv},
%      primaryClass={math.AG},
%      url={https://arxiv.org/abs/2103.07305}, 
%}


%\bib{Filt}{article}{%https://doi.org/10.48550/arxiv.1808.10162,
 % doi = {10.48550/ARXIV.1808.10162},
  
%  url = {https://arxiv.org/abs/1808.10162},
  
%  author = {Gil, José Ignacio Burgos and Mallick, Vivek Mohan},
  
%  keywords = {Algebraic Geometry (math.AG), Rings and Algebras (math.RA), FOS: Mathematics, FOS: Mathematics, 16W70, 14M25, 22E27},
  
%  title = {Multifiltrations},
  
%  publisher = {arXiv},
  
%  year = {2018},
  
%  copyright = {arXiv.org perpetual, non-exclusive license}
%}





%\bib{Alper}{article}{
%      title={Good moduli spaces for Artin stacks}, 
%      author={Jarod Alper},
 %     year={2009},
 %     eprint={0804.2242},
 %     archivePrefix={arXiv},
%      primaryClass={math.AG},
%      url={https://arxiv.org/abs/0804.2242}, 
%}



%\bib{NonRed}{article}{
%      title={Towards non-reductive geometric invariant theory}, 
%      author={Brent Doran and Frances Kirwan},
 %     year={2007},
%      eprint={math/0703131},
%      archivePrefix={arXiv},
%      primaryClass={math.AG},
%      url={https://arxiv.org/abs/math/0703131}, 
%}

%\bib{Conrad}{article}{
%  title={Reductive Group Schemes},
%  author={Brian Conrad},
 % year={2014},
%  url={https://api.semanticscholar.org/CorpusID:126011003}
%}

% \bib{Rob}{book}{
% author = {Roberts, Paul C.}, 
% place={Cambridge}, 
 %series={Cambridge Tracts in Mathematics}, 
 %title={Multiplicities and Chern Classes in Local Algebra}, 
 %DOI={10.1017/CBO9780511529986}, 
 %publisher={Cambridge University Press}, 
 %year={1998}, 
 %collection={Cambridge Tracts in Mathematics}}
 


%\bib{Sesh}{article}{
%    AUTHOR = {Seshadri, Conjeevaram Srirangachari},
%    TITLE = {Quotient spaces modulo reductive algebraic groups},
%    JOURNAL = {Ann. of Math. (2)},
%    FJOURNAL = {Annals of Mathematics. Second Series},
  %  VOLUME = {95},
  %  YEAR = {1972},
  %  PAGES = {511--556},
  %  ISSN = {0003-486X},
%}



%\bib{Cox2}{article}{
 %     title={The Functor of a Smooth Toric Variety}, 
 %    author={David A. Cox},
 %     year={1993},
 %     eprint={alg-geom/9312001},
 %     archivePrefix={arXiv},
  %    primaryClass={alg-geom},
  %    url={https://arxiv.org/abs/alg-geom/9312001}, 
%}

%\bib{Mukai}{book}{
%  title={An Introduction to Invariants and Moduli},
%  author={Mukai, S. and Oxbury, W.M.},
%  isbn={9780521809061},
%  lccn={2002023422},
%  series={Cambridge Studies in Advanced Mathematics},
%  url={https://books.google.de/books?id=oUcMZbiM7eAC},
%  year={2003},
%  publisher={Cambridge University Press}
%}