\ifdefined\standalonechapter
\documentclass[11pt]{article}

% --- Language ---
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

% --- Mathematics ---
\usepackage{amsmath, amssymb, amsthm}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{bbm}

% --- Layout and formatting ---
\usepackage{geometry}
\geometry{margin=1in}
\usepackage[
    colorlinks=false,
    pdfborder={0 0 1}
]{hyperref}
\usepackage{enumitem}

\usepackage{booktabs}

% --- Theorem environments ---
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}

% --- Numbering ---
\numberwithin{equation}{section}

% --- Commands ---
\newcommand{\R}{\mathbb{R}}
\newcommand{\norm}[1]{\left\|#1\right\|}
\newcommand{\dotH}[1]{\dot{H}^{#1}}
\newcommand{\BMO}{\mathrm{BMO}^{-1}}
\newcommand{\dx}{\,\mathrm{d}x}
\newcommand{\dt}{\,\mathrm{d}t}

\begin{document}


\begin{flushright}
\begin{minipage}{0.55\textwidth} % adjustable between 0.5–0.6
\small\itshape
This is the fourth of ten papers devoted to reflections on the Millennium Problem.  
It generalizes known results on the 3D Navier–Stokes equations based on previous studies.  
We hope that the presented material will be useful, and we would be grateful for your attention, verification,  
and participation in the further development of the topic.
\end{minipage}
\end{flushright}

\vspace{1.5em}

\begin{center}
    {\LARGE\bfseries {An \(\varepsilon\)\nobreakdash-free rank-6 decoupling estimate \\for the paraboloid surface}\par}
    \vspace{1em}
    {\large\bfseries Pylyp Cherevan\par}
\end{center}

\vspace{1em}

{\small\noindent\textbf{Abstract.}
For the paraboloid decomposition
\[
   F=\sum_{\Theta} F_{\Theta},
   \qquad
   \Theta\subset\{\lvert\xi\rvert\sim\lambda\},\;
   \operatorname{rad}(\Theta)=r=\lambda^{-2/3},
\]
we prove a log-free estimate
\[
   \|F\|_{L^{6}(Q_{\lambda})}\;\lesssim\;
   \lambda^{\Sigma_{\lambda}}\,
   D^{\Sigma_{D}}\,
   \Bigl(\sum_{\Theta}\|F_{\Theta}\|_{L^{6}}^{2}\Bigr)^{1/2},
   \qquad
   \Sigma_{\lambda},\Sigma_{D}<0,\;
   \lambda\to\infty ,
\]
where $D=\lambda^{1/12}$ and the cylinder $Q_{\lambda}$ is defined in~\eqref{eq:def-cylinder}.

\smallskip\noindent
\textbf{Key components of the argument}
\begin{itemize}
\item \emph{Broad geometry of rank 3.}  
      Bilipschitz behavior of normals gives  
      $\max_{i<j<k}\|n_{i}\wedge n_{j}\wedge n_{k}\|\gtrsim\lambda^{-5/4}$,  
      which through a trilinear Kakeya–BCT insertion contributes $+\tfrac{5}{36}$ in $\lambda$.
\item \emph{Kernel estimate.}  
      Twelve integrations (6 in $t$, 6 in $x'$) and measure analysis (Schur + TT$^\ast$)
      yield $\|K\|_{L^2\to L^2}\lesssim \lambda^{-9/2}D^{-3}$ (rows $-9/2$ in $\lambda$, $-3$ in $D$).
\item \emph{Robust-Kakeya.}  
      A density threshold $>c_*D$ brings a factor $D$  
      ($+\tfrac{1}{12}$ in $\lambda$, $+1$ in $D$).
\item \emph{Algebraic “shell.”}  
      Excluding a neighborhood $N_{\beta}(P)$ contributes $-\tfrac{1}{12}$ in $\lambda$ and $-1$ in $D$.
\item \emph{Tube packing.}  
      This section is explanatory; its contribution is not used in the final balance.
\item \emph{Narrow cascade.}  
      A double $7/8$ rescaling drives the flow out of the narrow regime and
      contributes a \emph{negative} $-\tfrac{5}{64}$ in $\lambda$ (zero in $D$).
\end{itemize}

\smallskip\noindent
\textbf{Summary of exponents.}
\[
\Sigma_\lambda=\frac{5}{36}-\frac{9}{2}-\frac{5}{64}
=-\frac{2557}{576}\approx -4.44<0,\qquad
\Sigma_D=-3+1-1=-3<0.
\]
The negativity of both sums removes the traditional $\lambda^\varepsilon$- and $D^\varepsilon$-losses.
}

% --- Contents ---
\tableofcontents
\fi

% --- Sections of the paper ---

\input{paper4_e-free/sections/01intro}
\input{paper4_e-free/sections/1notation}
\input{paper4_e-free/sections/2broad3}
\input{paper4_e-free/sections/3kernel}
\input{paper4_e-free/sections/4kakeya}
\input{paper4_e-free/sections/5ube-pack}
\input{paper4_e-free/sections/6alg-skin}
\input{paper4_e-free/sections/7narrow}
\input{paper4_e-free/sections/8balance}
\input{paper4_e-free/sections/9conclusion}

% --- Appendices ---
\appendix

\input{paper4_e-free/appendix/Adet}
\input{paper4_e-free/appendix/B}
\input{paper4_e-free/appendix/Cclarifications}
\input{paper4_e-free/appendix/Damp}

% --- Bibliography ---

\newpage

\cleardoublepage
\phantomsection
\addcontentsline{toc}{section}{References}
\bibliographystyle{unsrt}
\bibliography{commutator_refs}
\end{document}
\fi