\subsection{A colimit and a cylindrical contact flow category}\label{subsec:colimit-proof}
Our construction of global Kuranishi charts for the moduli spaces $\Mbar^{J}_{\sft}(\Gamma^+,\Gamma^-;\beta)_\Lambda$ requires us to approximate the contact form $\lambda$ by a $1$-form with integral action on the Reeb orbits in order to construct framings. This forces our construction of the flow category $\scM^{Y,\lambda}_{\le L}$ to depend on the action bound $L$. To obtain the ``full flow category'' of $(Y,\lambda)$ we take a colimit of the induced diagram of flow categories. Since we do not prove that the composition of our flow bimodules is (homotopic to) the flow bimodule of the `larger' cobordism, the full flow category will be a telescope of the flow categories of Theorem~\ref{thm:sft-flow-category}.

\begin{proposition}\label{prop:colimit-of-flow-cats}
    There is a directed system  \[ \scM^{Y,\lambda}_1 \rightarrow  \scM^{Y,\lambda}_2 \rightarrow \dots \] of the symmetric stably complex flow categories constructed in Theorem \ref{thm:flow-cat}. 
\end{proposition}

\begin{definition}
    We call the colimit $$\scM^{Y,\lambda} \coloneqq \colim\limits\,\scM^{Y,\lambda}_n$$ in $\Flow^{\Sigma,U}$ ``the" \emph{contact flow category} of the contact manifold $(Y,\lambda).$ 
\end{definition}   

While we expect $\scM^{Y,\lambda}$ to be independent of the required auxiliary choices, we do not show this invariance here.

\begin{proof} From the discreteness of $\spec(\lambda) \sub \bR$, we can find an order-preserving enumeration $a\cl \bN \to \spec(\lambda)$. We choose $\cP_L$-integral approximations by taking any $\cP_{a(1)}$-integral approximation $\wt\lambda_1$ and selecting the $\cP_{a(n+1)}$-integral approximation $\wt\lambda_n$ such that the action $\cA_{\wt \lambda_n}(\gamma)$ divides $\cA_{\wt \lambda_{n+1}}(\gamma)$ whenever $\cA_\lambda(\gamma) \leq a(n)$.
Choose prime integers $p_n$ so that for any $n\geq 1$, the pair $(p^+,p^-) = (p_{n+1},p_n)$ satisfies~\eqref{eq:primes-for-base}. Let $\wh X = \wh Y$ be the trivial cobordism equipped with the chosen almost complex structure $J$ and let $\scN^{n}_{\wh Y}$ be the bimodule associated to $(\wh X,J)$ and the following pre-perturbation datum $\fD^\pm_n$ given by
\begin{itemize} 
    \item $L^+ = a(n+1), L^- = a(n)$,
    \item $\cP^-_n = \cP_{a(n)}$ and $\cP^+_n = \cP_{a(n+1)}$,
    \item $p^+ = p_{n+1}$, $p^- = p_n$.
\end{itemize}
The bimodules $\scN^{n}_{\wh Y}$ induce the directed system $\scM^{Y,\lambda}_1 \;\stackrel{\scN^{1}_{\wh Y}}{\longrightarrow}\;  \scM^{Y,\lambda}_2\;\xrightarrow[]{\scN^{2}_{\wh Y}} \;\dots$ of the claim.\par
It remains to show that they admit stable complex structures compatible with those of $\scM^{Y,\lambda}_i$ from Theorem~\ref{thm:stable-complex-structure}.
Fix thus $i\in \bN$. By \cite[Definition~4.17]{AB24}, respectively its adaption to our setting, we have to construct for any function $\Lambda\cl \Gamma^-\to \Gamma^+$ between a sequence of Reeb orbits considered as objects of $\scM^{Y,\lambda}_i$ and $\scM^{Y,\lambda}_{i+1}$, respectively, the data of
\begin{enumerate}
    \item a complex virtual vector bundle $\wt I_\Lambda$
    \item a vector bundle $\wt W_\Lambda$
    \item the vector space $\wt U_\Lambda = (\bR,\bR^{\{\Gamma^+\}})$
\end{enumerate}
 on $\scN^i_\Lambda\coloneqq\scN^i_Y(\Gamma^-,\Gamma^+)_\Lambda$ together with an equivalence
 \begin{equation}
     T\scN^i_\Lambda\,\oplus\, V^i_{\Gamma^+} \,\oplus\, \wt W_\Lambda\ \cong\ \wt I_{\Lambda}\,\oplus\, \wt U_\Lambda\,\oplus\, \wt{W}_\Lambda\,\oplus\,V^{i+1}_{\Gamma^+}
 \end{equation}
 where $V^j_\Gamma$ is the vector bundle constructed in \S\ref{subsec:lift-of-objects} with the perturbation data used for $\scM^{Y,\lambda}_j$. These are required to satisfy analogues of the compatibility conditions described in Definition~\ref{de:stable-complex-flow-cat}. As in \textsection\ref{subsec:stable-complex}, the construction of such a stably complex lift of $\scN^{\wh Y}_i$ can be split up into the construction of stable complex structures on the base spaces, cf. Lemma~\ref{lem:stable-complex-base}, and those on the vertical tangent bundle. The generalization of Lemma~\ref{lem:stable-complex-base} to the cobordism base spaces is straightforward, because the key input, Lemma~\ref{lem:stable-complex-corner-blow-up}, is a general statement that also holds for cobordism base spaces. The construction of the stable complex structures on the vertical tangent bundles is exactly the same as in \S\ref{subsec:stable-complex-fiber}. The only difference is that we have $T^v\scN^i_\Lambda = \ker(D(\delbar_J) + \mu_\Lambda)$, while $T^v\scM^{Y,\lambda}_i\oplus  \bR = \ker(D(\delbar_J) + \mu_\Lambda)$ due to the fact that we quotient by translations in the target for curves in the symplectization. This accounts for the difference between $U_\Lambda$ and $\wt U_\Lambda$. Choosing the auxiliary data needed for the construction of the stable complex structures inductively, their compatibility with the composition maps in the sense of Proposition~\ref{prop:existence-stable-complex} follows. 
\end{proof}

In the construction of the full contact flow category above, we were forced to take the colimit approach due to a lack of an integral approximation $\wt \lambda$ without first filtering through the action. However, we can construct a flow category for cylindrical contact homology directly. We collect the necessary modifications to obtain a cylindrical contact flow category.


\begin{theorem}\label{thm:cyl-flow-cat}
    Let $(Y,\lambda)$ be a hyper-tight contact manifold with a given compatible almost complex structure $J$ interpolating between cylindrical almost complex structures $J^\pm$. Then, there exists a flow category $\scM_{cyl}$ of class rel--$C^1$ whose objects are the Reeb orbits of $\lambda$ and whose morphism spaces are 
    \begin{equation*}\label{eq:morphisms-cylindrical}
        \scM_{cyl}^{Y,\lambda}(\gamma^-,\gamma^+) = \Mbar_{\sft}^{\, J}(\gamma^+,\gamma^-)
    \end{equation*}
    for any pair $(\gamma^+,\gamma^-)$ of Reeb orbits.
\end{theorem}

\begin{proof}
Recall that the construction of the global Kuranishi charts in \S\ref{subsec:construction} started off with a choice of a pre-perturbation datum $\fD = (\wt\lambda,\conn,p)$ as in Definition~\ref{de:pre-perturbation}. The integral approximation $\wt \lambda$ was only used to frame holomorphic buildings; cf. \S\ref{sssec:framings_of_buildings}. We can instead use the following scheme to frame cylindrical holomorphic buildings. Let $$\cA_e\cl \spec(\lambda) \to \bN$$ denote the ordered enumeration function on the spectrum of the contact form $\lambda$. Given a cylindrical holomorphic building $u$, we replace the complex line bundle in \eqref{eq:linebundle-construction} with the following cylindrical version
\begin{equation}\label{eq:cyl-linebundle-construction}
	L^c_{u_v} \coloneqq \cO_{C_v}\lbr{{\cA_e(\gamma_{e^+}) \; z_{v,e^+}} - {\cA_e(\gamma_{e^-})\; z_{v,e^-}}}^{\otimes p}.
\end{equation}
We use sections of such line bundles to frame cylindrical buildings. The map 
\begin{gather}
    E\cl \Mbar_{\sft}^J(\gamma^+,\gamma^-)^{cyl} \to \bN  \\
    [u] \mapsto \cA_e(\gamma^+) - \cA_e(\gamma^-)
\end{gather}
that sends a cylindrical holomorphic building to the difference of $\cA_e$-action of the incoming and outgoing Reeb orbit, satisfies the following properties:
\begin{itemize}
    \item $E$ is additive under cylindrical breaking, i.e., $E([u_1]\#[u_2])  =  E([u_1]) + E([u_2]), $
    \item $E\geq 0$ and $E([u])=0$ if and only if $[u]$ is a trivial cylinder.
\end{itemize}
    The proof of Theorem~\ref{thm:flow-cat} now carries over verbatim except for replacing every mention of $\cA_{\wt \lambda}$ with $\cA_{e}$, using the line bundles of \eqref{eq:cyl-linebundle-construction}, and assuming that each $\Gamma$ is a singleton set.
\end{proof}