We can now prove Theorem~\ref{thm:pardon-gkc}\eqref{gkc-rel-smooth}. Let $\alpha$ be a perturbation datum. We use the same notation as above. Write $\beta \cl \cBR\to \cB$ for the forgetful map.

\begin{proposition}\label{prop:pre-thickening-smooth} The forgetful map $\cT\to \cBR$ is a $G$-equivariant $C^1_{loc}$-fiber bundle. In particular, it is a topological submersion whose fibers carry a canonical smooth structure. 
\end{proposition}

\begin{proof}This follows from Theorem~\ref{thm:gluing-main} and Proposition~\ref{prop:c1loc}.
\end{proof}


\begin{lemma}\label{lem:group-action} The action $G\times \cT/G\times \cBR\to \cT/\cBR$ is fiberwise locally linear and of class rel--$C^1$.
\end{lemma}

\begin{proof} The action map is continuous by the definition of the topology on $\cT$. The fact that it is of class rel--$C^1$ follows from the gluing result in \textsection\ref{sec:gluing}, while the fiberwise local linearity is a consequence of relative $C^1$-regularity and the same argument as in \cite[Lemma~5.9]{HS22}.
\end{proof}

\begin{lemma}\label{lem:zero-locus-correct} The forgetful map $\fs_{\text{pre}}\inv(0)\to \Mbar^J(T)$ descends to an isomorphism $$\fs_{\text{pre}}\inv(0)/G\,\cong\, \Mbar^J(T)$$ 
    of orbispaces.
\end{lemma}

\begin{proof} By Lemma~\ref{lem:zero-locus-right}, it suffices to show that $\fs_{\text{pre}}\inv(0)/G\,\cong\, \cZ_{\delbar}/\cG$. This follows from the $\cG$-equivariance of $\zeta_\cU$.
\end{proof}

The obstruction bundle $\cE$ is trivially of class rel--$C^1$; however, the obstruction section $\fs_{\text{pre}}$ is only continuous since the cut-off functions we construct in \textsection\ref{subsec:domain-metrics} are only continuous. 

\begin{lemma}\label{lem:better-obstruction-section} We can replace $\fs_{\text{pre}}$ by a $\wh G$-equivariant obstruction section $\fs$ of class rel--$C^1$ with $$\fs_{\text{pre}}\inv(0) = \fs\inv(0).$$
\end{lemma}

\begin{proof} We only have to replace the projection of $\fs_{\text{pre}}$ to the second summand. This follows from a mollification argument as in \cite[Lemma~4.55]{AMS23}.
\end{proof}


