\section{Moduli spaces of pseudo-holomorphic buildings}

\subsection{Background}\label{subsec:background}
Let $(Y^{2n-1},\xi)$ be a closed contact manifold equipped with a contact form $\lambda$, i.e., a $1$-form satisfying $\ker(\lambda) = \xi$ and $\lambda \wedge (d\lambda)^{n-1} > 0$. Let $R$ be the associated Reeb vector field, uniquely determined by the conditions 
$$d\lambda(R,\cdot) = 0 \qquad \qquad \lambda(R) = 1.$$
Its closed orbits are called Reeb orbits. We define
	$$\cP_1\coloneqq \cP_1(\lambda) := \modulo{\set{\gamma\in C^\infty(S^1,Y)\mid\exists T > 0 : \dot{\gamma} = T\,R(\gamma)}}{\sim}$$
    to be the set of unparametrized Reeb orbits of constant speed of $\lambda$. Let $\cP^*_1\sub \cP_1$ be the subset of simple Reeb orbits. Given $\gamma\in \cP_1$, we denote by 
	\begin{itemize}
		\item $\multr{\gamma}$ the multiplicity of $\gamma$,
		\item $\cc{\gamma}$ the underlying simple orbit and identify it with $\im(\gamma)$,
        \item $\wt\gamma$ any parametrization of $\gamma$,
            \item $\cA(\gamma) := \int_{S^1}\gamma^*\lambda$ the \emph{action} of $\gamma.$
	\end{itemize}
We assume that $\lambda$ is \emph{nondegenerate}, that is, that the return map $d\phi_R^T(\gamma(1))$ of the Reeb flow has no eigenvalue $1$ for a Reeb orbit $\gamma$ of action $T$. Equivalently, the set of simple unparametrized Reeb orbits is discrete in $Y$.

An almost complex structure $J$ on the \emph{symplectization} $(\wh Y,\omega)\coloneqq (\bR \times Y,d(e^s\lambda))$ is \emph{$\lambda$-adapted} if $J$ is invariant under the $\bR$- translation action, $J(\frac{\partial}{\partial t}) = R $ and $J|_\xi$ tames $d\lambda$. Any $d\lambda$-compatible almost complex structure $J_\xi$ on $\xi$ determines uniquely a $\lambda$-adapted almost complex structure $J$ on the symplectisation $\wh Y$.\par
A smooth map
$u\cl \dot C \to \bR \times Y$ on a punctured Riemann surface $(\dot{C},\fj)$ is \emph{$ J$-holomorphic} if it satisfies the Cauchy-Riemann equation $$\delbar_{ J} u \coloneq \frac12(du + J du \fj) = 0.$$ 
Note that due to exactness, all $J$-holomorphic maps from a closed Riemann surface to the symplectization are constant. The simplest type of non-constant $J$-holomorphic curves is given by \emph{trivial cylinders}. They are of the form $$u_\gamma\cl\bR \times S^1 \to \bR \times Y: (s,t)\mapsto (Ks,\wt\gamma(Kt)),$$
for some Reeb orbit $\gamma$ and a constant-speed parametrization $\wt\gamma$ of $\gamma$, where $K = \int_\gamma\lambda$ is the action of the Reeb orbit.\par 
Since $\wh Y$ is non-compact and the curves are punctured, the usual notion of energy does not make sense in this context. The analogue is the \emph{Hofer energy}, given by 
$$E_H(u) = \int_{\dot C} f ^* d\lambda + \sup_{\phi \in \cC}\int a \;da\wedge f^*\lambda $$ 
for map $u=(a,f)\cl \dot{C}\to \wh Y$, where $\cC$ is the set of non-negative smooth functions $\phi : \bR \to \bR$ with compact support and normalized $L^1$ norm (i.e., $\int_\bR \phi(s) ds = 1.)$  In the case of non-degenerate contact form $\lambda$, it follows from \cite{HWZI} that any $J$-holomorphic curve with finite Hofer energy asymptotically converges to a trivial cylinder over a Reeb orbit.\par
The compactness result \cite[Theorem 10.1]{BEH03} (or \cite{CM05}) proves that the moduli space of punctured curves with bounded Hofer energy and bounded topological type allows a natural compactification by adding boundary strata of $J$-holomorphic buildings. We will now discuss them in detail in genus zero.





